### 2025-01-16 skripsi/chapter4.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and lacheck complaints

\begin{figure}[H]
  \centering
  \begin{lstlisting}[language=Python]
  import xarray as xr
  ds = xr.open_zarr(
      "DATASET_ADDRESS",
      storage_options = {"token": "anon"},
  )
  \end{lstlisting}
  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
\end{figure}

The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively. The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}. The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}. The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019. This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.

@@

The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere. For our use, we will only be using the 2-meter temperature of the atmosphere. This is the air temperature 2 meters above the surface be it land, sea, or inland water. This variable is in units of kelvin (K). Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level. An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}. The data shown is in the equiangular projection. This means that towards the poles, the shapes become more distorted. While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data. To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
\begin{figure}[H]
  \centering
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/wb2_train_data.pgf}
    \end{adjustbox}
    \caption{2-meter temperature}\label{fig:wb2_train_data}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/wb2_clim_data.pgf}
    \end{adjustbox}
    \caption{Climatology}\label{fig:wb2_clim_data}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/wb2_train_anomaly.pgf}
    \end{adjustbox}
    \caption{2-meter temperature anomaly}\label{fig:wb2_train_anomaly}
  \end{subfigure}
  \caption{Data retrieved:(\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@. (\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@. (\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.}\label{fig:wb2_data}
\end{figure}

@@

\subsection{Design}\label{sec:implementation_design}
\noindent In this subsection, the architectural design of the software product is explained. The architecture consists of modules with similar concerns. This was chosen because of the intuition built by the use of other libraries with a similar architecture. The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, and basis functions. Each of these concerns are addressed by a corresponding module. The explanation of each module are as follows:
\begin{enumerate}
  \item Utilities

        \noindent This module provides basic tools that are used across the entire library. The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers. Scaling functionality is used for inputs into the support vector machines. And as previously mentioned, since LSSVR only works with real numbers, the tools for converting between complex and their real number representations is also necessary. Another useful tool for working with basis coefficients is a way to resize the coefficients in terms of how many basis functions is desired. An example of the usage is downsizing Fourier coefficients from 12 to 8 modes. The last utility mentioned here provides the ability to solve ordinary differential equations. This utility is useful for generating data for certain types of PDEs such as the Burgers' equation.

  \item Basis Functions

        \noindent As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves. The module will define the functionality and data structure that is expected to be used when working with basis functions in this library. First and foremost, the central function of this module is to store and facilitate the connection between the coefficients in the spectral domain and their values in the physical domain. This is dependent on the basis functions used. For the Fourier basis that we use in this study, this means that the transformations are the discrete Fourier transform and the discrete inverse Fourier transform. Other than this core functionality, information on the characteristics of the coefficients such as the number of modes, in other words basis functions, should also be provided by this module. In addition, other functionality included in this module are visualization of coefficients in physical space, generation of random functions, time dependent \& complex/real coefficients, noise perturbation of functions, and differential operators.

  \item Model

        \noindent The proposed SpectralSVR model is implemented in this module. As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study. The SpectralSVR wrapper must provide three core pieces of functionality. First, it must translate complex input and output samples into their real representations. This applies to both training and evaluation. Second, in addition to predicting the coefficients during evaluation, the wrapper should also be able to predict the function values themselves for any given set of point coordinates. This is important for quick evaluations of a predicted function at an arbitrary point. The third functionality is inverse input function search for a given output. This is useful for inverse problems where the parameters are unknown, but the solution is partially known. Aside from the core functionality, a complementary functionality is testing for the learned model.

@@

  \item Problems

        \noindent This module provides the functionality concerned with generating data. Two out of the three datasets in this study are generated with this module. In general this module provides two pieces of functionality. The first is generation of the data itself. This functionality generates at least two sets of functions that are related to each other by the chosen PDE\@. The generation is based on at least two parameters which are the number of samples to generate and the number of modes or basis functions to generate the coefficients for. The second functionality provided by this module is the residual based on the chosen PDE\@. This is useful to verify if any set of functions comply with the PDE\@. For example, the residual may be used to verify the generated data. Another use is to grade the predictions by the learned model.

>>>>

\begin{figure}[H]
  \centering
  \begin{lstlisting}[language=Python]
  import xarray as xr
  ds = xr.open_zarr(
      "DATASET_ADDRESS",
      storage_options = {"token": "anon"},
  )
  \end{lstlisting}
  \caption{Example of using Xarray to access a publicly accessible Zarr dataset hosted on Google Cloud Storage Bucket.}\label{fig:access_remote_zarr}
\end{figure}
% ignore chktex warnings about the URLs
The specific dataset resolution we use is 64 by 32 representing longitude and latitude respectively. The ERA5 reanalysis dataset is hosted at the following URL\@: \url{gs://weatherbench2/datasets/era5/1959-2023_01_10-6h-64x32_equiangular_conservative.zarr}. The corresponding climatology is hosted at \url{gs://weatherbench2/datasets/era5-hourly-climatology/1990-2019_6h_64x32_equiangular_conservative.zarr}. The climatology is the average for hours 0, 6, 12, and 18 for each day of the year from 1990 until 2019. This average helps in defining the expected state of the weather at specific points in time based on the historical averages for that time of day and year.

@@

The dataset includes 62 variables with some variables also spanning 13 discrete vertical levels in the atmosphere. For our use, we will only be using the 2-meter temperature of the atmosphere. This is the air temperature 2 meters above the surface be it land, sea, or inland water. This variable is in units of kelvin (K). Vertically, the values of this variable is obtained by interpolating between the model values at the surface and the lowest model vertical level. An example of the data that was retrieved can be seen in \lccref{fig:wb2_data}. The data shown is in the equiangular projection. This means that towards the poles, the shapes become more distorted. While this is not the most ideal way to represent the data, using the data in this way adds to the challenge of how the model can adapt to the use of suboptimal configurations in the data. To compute the anomaly, we can simply subtract the current state in \lccref{fig:wb2_train_data} by the climatology in \lccref{fig:wb2_clim_data} resulting in \lccref{fig:wb2_train_anomaly}.
\begin{figure}[H]
  \centering
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/wb2_train_data.pgf}
    \end{adjustbox}
    \caption{2-meter temperature}\label{fig:wb2_train_data}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/wb2_clim_data.pgf}
    \end{adjustbox}
    \caption{Climatology}\label{fig:wb2_clim_data}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/wb2_train_anomaly.pgf}
    \end{adjustbox}
    \caption{2-meter temperature anomaly}\label{fig:wb2_train_anomaly}
  \end{subfigure}
  \caption{Data retrieved: (\subref{fig:wb2_train_data}) 2-meter temperature at January 1, 1995 6:00 UTC\@. (\subref{fig:wb2_clim_data}) 2-meter temperature climatology for the first day of the year at hour 6 UTC\@. (\subref{fig:wb2_train_anomaly}) Anomaly for 2-meter temperature at January 1, 1995 6:00 UTC\@.}\label{fig:wb2_data}
\end{figure}

@@

\subsection{Design}\label{sec:implementation_design}
\noindent In this subsection, the architectural design of the software product is explained. The architecture consists of modules with similar concerns. This was chosen because of the intuition built by the use of other libraries with a similar architecture. The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, and basis functions. Each of these concerns are addressed by a corresponding module. The explanation of each module are as follows:
\begin{numdesc}
  \item[Utilities]
  This module provides basic tools that are used across the entire library. The utilities this module needs to provide include scaling, conversion between real and complex representations of matrices, resizing coefficient tensors, and adaptors for or the traditional ordinary differential equation solvers. Scaling functionality is used for inputs into the support vector machines. And as previously mentioned, since LSSVR only works with real numbers, the tools for converting between complex and their real number representations is also necessary. Another useful tool for working with basis coefficients is a way to resize the coefficients in terms of how many basis functions is desired. An example of the usage is downsizing Fourier coefficients from 12 to 8 modes. The last utility mentioned here provides the ability to solve ordinary differential equations. This utility is useful for generating data for certain types of PDEs such as the Burgers' equation.

  \item[Basis Functions]
  As the proposed model will learn the relationships defined by PDEs within the spectral domain, a large proportion of the computation will also concern the use of the basis functions themselves. The module will define the functionality and data structure that is expected to be used when working with basis functions in this library. First and foremost, the central function of this module is to store and facilitate the connection between the coefficients in the spectral domain and their values in the physical domain. This is dependent on the basis functions used. For the Fourier basis that we use in this study, this means that the transformations are the discrete Fourier transform and the discrete inverse Fourier transform. Other than this core functionality, information on the characteristics of the coefficients such as the number of modes, in other words basis functions, should also be provided by this module. In addition, other functionality included in this module are visualization of coefficients in physical space, generation of random functions, time dependent \& complex/real coefficients, noise perturbation of functions, and differential operators.

  \item[Model]
  The proposed SpectralSVR model is implemented in this module. As the proposed model essentially wraps a support vector regression model in such a way that it can process coefficients, this module will house the SpectralSVR wrapper itself and the LSSVR variant of support vector regression that is used in this study. The SpectralSVR wrapper must provide three core pieces of functionality. First, it must translate complex input and output samples into their real representations. This applies to both training and evaluation. Second, in addition to predicting the coefficients during evaluation, the wrapper should also be able to predict the function values themselves for any given set of point coordinates. This is important for quick evaluations of a predicted function at an arbitrary point. The third functionality is inverse input function search for a given output. This is useful for inverse problems where the parameters are unknown, but the solution is partially known. Aside from the core functionality, a complementary functionality is testing for the learned model.

@@

  \item[Problems]
  This module provides the functionality concerned with generating data. Two out of the three datasets in this study are generated with this module. In general this module provides two pieces of functionality. The first is generation of the data itself. This functionality generates at least two sets of functions that are related to each other by the chosen PDE\@. The generation is based on at least two parameters which are the number of samples to generate and the number of modes or basis functions to generate the coefficients for. The second functionality provided by this module is the residual based on the chosen PDE\@. This is useful to verify if any set of functions comply with the PDE\@. For example, the residual may be used to verify the generated data. Another use is to grade the predictions by the learned model.

\end{numdesc}

### 2025-01-16 skripsi/chapter5.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and lacheck complaints

\section{Conclusion}
\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
\begin{enumerate}
    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs. This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.
    \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
    \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
\end{enumerate}
% \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan. Simpulan ini menyajikan sejumlah hal penting yang disampaikan secara ringkas, padat, dan utuh, yang menjawab tujuan penelitian yang dituliskan pada Bab Pendahuluan. Sangat mungkin   ada beberapa konsekuensi dan implikasi yang ditimbulkan dari simpulan yang dihasilkan, yang sepatutnya menjadi perhatian pada penelitian berikutnya. Judul bab dapat disesuaikan, namun umumnya ada \textit{Simpulan} yang memang mendominasi isi bab ini.

>>>>

\section{Conclusion}
\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
\begin{enumerate}
    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs. This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.\@\item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
    \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
\end{enumerate}
% \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan. Simpulan ini menyajikan sejumlah hal penting yang disampaikan secara ringkas, padat, dan utuh, yang menjawab tujuan penelitian yang dituliskan pada Bab Pendahuluan. Sangat mungkin   ada beberapa konsekuensi dan implikasi yang ditimbulkan dari simpulan yang dihasilkan, yang sepatutnya menjadi perhatian pada penelitian berikutnya. Judul bab dapat disesuaikan, namun umumnya ada \textit{Simpulan} yang memang mendominasi isi bab ini.
